MCTS Applied to Co-operative Problems

### 2015-07-04 Report/ceec.tex
Reworked the R file for making graphs with filenames that can be read by latex
Worked latex to read from either of the maps directories
Changed the old graphs to a new file name so that latex gets the correct new ones
Widened the graphs a little - changed the csv file I was using to include VariGA instead of the really long name which fixed the graphs. Some minor extra writing in the document

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{level1vsleve1e}
\caption{Graph showing the average score obtained by each \emph{Agent} across level 1(Blue) and level 1E (Orange)}
\label{1v1eS}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{level1vsleve1eTicks}
\caption{Graph showing the average ticks taken for each \gls{ai} \emph{Agent} across level 1(Blue) and level 1E (Orange)}
\label{1v1eT}
\end{figure}

Figure \ref{1v1eS} shows the effect that having the complex \emph{Buttons} and \emph{Doors} in a level has on the score an Agent achieves. Figure \ref{1v1eT} demonstrates the vast improvement in path finding ability to a goal in the VariGA compared to the GAController. This is expected due to the ability to make individual actions as compared to the GAController which is only able to make 3 identical turns at a time leading to convoluted paths compared to optimum.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{avgScoreOverAllMaps}
\caption{Average score of each AI Agent over all the Maps}
\label{avgScoreAllMaps}
\end{figure}

Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps. The two more powerful \gls{mcts} Agents performed the best, doing much better than the competition. Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks. \emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{avgTicksOverAllMaps}
\caption{Average Ticks taken for each AI Agent over all the Maps}
\label{avgTicksAllMaps}
\end{figure}

\pagebreak
\begin{figure}[ht]
\centering
\includegraphics[scale=0.5]{level5}
\caption{The initial starting state for level5.txt}
\label{Level5State}
\end{figure}
Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}). The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents. Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance. The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over $0.8$.

\begin{figure}[ht]
\centering
\includegraphics[ width = \linewidth]{avgScoreOverMap5}
\caption{Average Score for each AI agent over Map 5}
\label{avgScoreMap5}
\end{figure}

@@

\subsection{Further Work}
There is scope for more work in a number of areas. More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves. A framework for communication would be devised - with the requirement for fairly \gls{ggp} restrictions in mind.

>>>>

\graphicspath{{stats-processing/}{stats-processing/data/maps/}}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{level1E-txt-pairs-ticks}
\caption{Average ticks taken to complete level1E.txt when paired only with identical Agents}
\label{1epairedTicks}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{level1-txt-pairs-ticks}
\caption{Average ticks taken to complete level1.txt when paired only with identical Agents}
\label{1pairedTicks}
\end{figure}

Figure \ref{1epairedTicks} shows the ability of each Agent to solve a simple path finding problem. The \emph{GAcontroller}, with its macro actions, is hindered by its inability to make single step moves and has trouble actually walking straight to the target. The \emph{VariGA} does significantly better, due to its ability to perform single step moves. Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added. This proves that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the tasks.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{scores-allmaps}
\caption{Average score of each AI Agent over all the Maps}
\label{avgScoreAllMaps}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{ticks-allmaps}
\caption{Average Ticks taken for each AI Agent over all the Maps}
\label{avgTicksAllMaps}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{scores-samepairs}
\caption{Average Scores for each AI Agent paired with itself over all the Maps}
\label{avgScorePairAllMaps}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{ticks-samepairs}
\caption{Average Ticks taken for each AI Agent paired with itself over all the Maps}
\label{avgTicksPairAllMaps}
\end{figure}

Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps. The two more powerful \gls{mcts} Agents performed the best, doing much better than the competition. Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks. \emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks. Comparing the \gls{ai} \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}. The shockingly good results for \emph{RandomController} are potentially due to the fact that the 3 \gls{mcts} controllers and 2 \gls{ga} algorithms all based their decisions on having Random as an accomplice.

\pagebreak
\begin{figure}[ht]
\centering
\includegraphics[scale=0.5]{level5}
\caption{The initial starting state for level5.txt}
\label{Level5State}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width = \linewidth]{level5-txt-scores}
\caption{Average Score for each AI agent over Map 5}
\label{avgScoreMap5}
\end{figure}

Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}). The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents. Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance. The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over $0.8$.

@@

\subsection{Further Work}
There is scope for more work in a number of areas. More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves. A framework for communication would be devised - with the requirement for fairly \gls{ggp} like restrictions in mind.
